---
title: "Chapter11"
author: "Victor Yim"
date: "November 13, 2016"
output: html_document
---
##This is data from Salesforce.com stock (Ticker: CRM) closing price for the last 12 months

getwd()  
setwd('C:/Users/Victor Yim/Downloads')  
getwd()  
CRM<- read.csv("C:\\Users\\Victor Yim\\Downloads\\CRM.csv", header = TRUE)  
Vol<-function(d,logrets)   
{  
  var=0  
  lam=0  
  varlist <-c()  
  for (r in logrets){  
    lam = lam*(1-1/d) + 1  
    var = (1 - 1/lam)*var + (1/lam)*r^2  
    varlist<-c(varlist, var)  
  }  
  sqrt(varlist)  
}  
CRMTS<-ts(CRM)  
head(CRM)  
length(CRM)  
CRMret <- log(lag(CRMTS))-log(CRMTS)  
CRMVol <- sd(CRMret) * sqrt(250)*100  
CRMVol  
volest<-Vol(10,CRMret)  
volest2<-Vol(30,CRMret)  
volest3<-Vol(100,CRMret)  
```{r setup, include=FALSE}
getwd()
setwd('C:/Users/Victor Yim/Downloads')
getwd()
CRM<- read.csv("C:\\Users\\Victor Yim\\Downloads\\CRM.csv", header = TRUE)
Vol<-function(d,logrets)
{
  var=0
  lam=0
  varlist <-c()
  for (r in logrets){
    lam = lam*(1-1/d) + 1
    var = (1 - 1/lam)*var + (1/lam)*r^2
    varlist<-c(varlist, var)
  }
  sqrt(varlist)
}
CRMTS<-ts(CRM)
head(CRM)
length(CRM)
CRMret <- log(lag(CRMTS))-log(CRMTS)
CRMVol <- sd(CRMret) * sqrt(250)*100
CRMVol
volest<-Vol(10,CRMret)
volest2<-Vol(30,CRMret)
volest3<-Vol(100,CRMret)


plot(volest,type="l")
lines(volest2,type="l", col="red")
lines(volest3,type="l", col="blue")
```



```{r CRMret}
#this is the Return of CRM
summary(CRMret)
```

```{r}
#plot for 3 level of weight at 10 / 30 /100
#plot(volest,type="l")
#lines(volest2,type="l", col="red")
#lines(volest3,type="l", col="blue")
```

```{r pressure, echo=FALSE}
plot(volest,type="l")
lines(volest2,type="l", col="red")
lines(volest3,type="l", col="blue")
```

